Latent Dirichlet Allocation Time Series (LDATS)

### 2018-10-26 inst/doc/LDATS.Rmd

---
title: "LDATS Example"
author: "Juniper L. Simonis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

This vignette walks through an example of **LDATS** at the command line and
was constructed using **LDATS** version `r vers` on `r today`.

@@

## Data

For this vignette, we will be using rodent data from the control plots of the
[Portal Project](https://github.com/weecology/portaldata), which come with
the **LDATS** package

```{r}
data(rodents)
rodents
```

>>>>

---
title: "Latent Dirichlet Allocation Time Series (LDATS)"
author: "Juniper L. Simonis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

## Overview

This vignette details the code base for the **LDATS** package. It was
constructed using **LDATS** version `r vers` on `r today`.

@@

## Analytical Pipeline

* `LDA_TS()`
  * `LDA_set()`
    * `LDA()`
  * `select_LDA()`
  * `TS_set_on_LDA()`
  * `select_TS()`
